CODECHECK: An open-science initiative to facilitate sharing of computer programs and results presented in scientific publications.

### 2020-09-30 codecheck-paper.tex
add tools and resources description

To run the system, we rely on github to host our work, and use a
custom R pacakge, codecheck, to help with the generation of
certificates and depositing work on zenodo. (Cite zen4R).  You can do
everything with open infrastructure (e.g.~automated rendering of
register). but you can use your own tools if you prefer.

>>>>

To run the system, we rely on freely available infrastructure, more 
specifically GitHub and Zenodo.

The \texttt{codecheckers} GitHub organisation\footnote{
\url{https://github.com/codecheckers}} contains projects managing the
project website, the community of codecheckers, community discussions,
forks of codechecked code repositories, and the main register for
managing the collection of checks. Both the website\footnote{
\url{https://codecheck.org.uk/}} and the register
\footnote{\url{https://codecheck.org.uk/register}} are hosted as GitHub
pages. The register is effectively a single table in CSV format that
connects the certificate identifier with the repository associated with
a specific conducted codecheck. Each of these repositories, which 
currently can be hosted on GitHub or Open Science Framework (OSF), 
contains the CODECHECK metadata file \texttt{codecheck.yml}. The register
further contains a column for the type of check, e.g., community, journal,
or conference, and the respective GitHub issue where communications and 
assignments around a specific check are organised. No information is 
duplicated between the register and the metadata files. When a new
certificate is entered into the register, an automated process using 
continuous integration infrastructure of GitHub, GitHub Actions, retrieves
the metadata files and builds different representations of the register
for viewing (HTML) or integration with other services (CSV, JSON).

Zenodo is an open repository for scientific data and documents. It
mints DOIs for deposits and ensures long-term availability of all digital
artefacts related to the project. These include the community 
certificates as well as the register, which is regularly archived to 
Zenodo \cite{codecheck_register} (including all file formats).

A custom R package, \texttt{codecheck}\footnote{
\url{https://github.com/codecheckers/codecheck}} helps with the generation
of certificates and depositing certificates and reated files on Zenodo 
using the R package \texttt{zen4R} \cite{zen4r}.
Codecheckers may choose to not use the package and rely on their own tools
for creating the certificate. This is a deliberate flexibility to
accomodate both different skill sets and unforseen technical advances or
challenges.

These tools and resources demonstrate that a CODECHECK process can be
managed without infrastructure costs on freely available platforms.
The scripted and automated parts should also ensure that more checks can
be conducted in the future.
The remaining costs are the project's domain, which is negligible, and
the human resources for managing the project and processes, which are
considerable and currently soley based on, partly grant-based, public funding.
Naturally, similar set-ups are possible, such as using GitLab/GitLab.com 
and the GitLab CI instead of GitHub and GitHub Actions, or using a different 
data repository for depositing certificates and data.
